---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# citationcheckR

<!-- badges: start -->
<!-- badges: end -->

The goal of `citationcheckR` is to make citing multiple package a little bit easier. Instead of having to copy and paste multiple citations, you can use it to create multiple citations at once. The package also includes functions which check citations to see if they are correct or not. 

## Installation

The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("matthewwankiewicz/citationcheckR")
```

## After using the Functions

Once you have created your citations and have them stored in another file, you will need to make changes to the YAML in your R Markdown file by adding two lines of text. The first line should say `bibliography: references.bib` or the name for your citation file, this will tell R where your citations are located. 

The other line you can include is `nocite: '@*'`. This will automatically add the citations found in your citation file to your R Markdown document. If you plan to cite each package in the body of your paper you don't need to include this line.

Example of the YAML header to include citations:

```{r eval=FALSE}
title:

author:

bibliography: references.bib

nocite: '@*'
```

## Issues

If you find any issues while using the package, please report it as an issue on the GitHub page and I'll get back to you as soon as possible.

