---
title: "The `check_bibtex_file` function"
author: "Matthew Wankiewicz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The `check_bibtex_file` function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(citationcheckR)
```

## About the Function

After you have finished filling up your citation and file and want to check if the citations are correct, `check_bibtex_file` is very useful. This function is a mix between the `check_bibtex_citations` and `check_citation_file` functions. It will go through the citation file and return any issues with the citations given.

## Using the function

### No Issues

For this example, we will use an example file which contains citations for `Lahman`, `tidyverse` and R:

```{r file, eval=FALSE}
@Manual{,
  title = {Lahman: Sean 'Lahman' Baseball Database},
  author = {Michael Friendly and Chris Dalzell and Martin Monkman and Dennis Murphy},
  year = {2021},
  note = {R package version 9.0-0},
  url = {https://CRAN.R-project.org/package=Lahman},
}

@Article{,
  title = {Welcome to the {tidyverse}},
  author = {Hadley Wickham and Mara Averick and Jennifer Bryan and Winston Chang and Lucy D'Agostino McGowan and Romain François and Garrett Grolemund and Alex Hayes and Lionel Henry and Jim Hester and Max Kuhn and Thomas Lin Pedersen and Evan Miller and Stephan Milton Bache and Kirill Müller and Jeroen Ooms and David Robinson and Dana Paige Seidel and Vitalie Spinu and Kohske Takahashi and Davis Vaughan and Claus Wilke and Kara Woo and Hiroaki Yutani},
  year = {2019},
  journal = {Journal of Open Source Software},
  volume = {4},
  number = {43},
  pages = {1686},
  doi = {10.21105/joss.01686},
}

@Manual{,
  title = {R: A Language and Environment for Statistical Computing},
  author = {{R Core Team}},
  organization = {R Foundation for Statistical Computing},
  address = {Vienna, Austria},
  year = {2019},
  url = {https://www.R-project.org/},
}
```

```{r no-issues}
check_bibtex_file("example.bib", c("Lahman", "tidyverse", "base"))
```

The function will go through each package citation and tell you if there are any issues. To avoid any confusion, it will tell you which package it is checking before returning any issues.

### Issues in two of three packages

For this example, we will use an example file which contains citations for `Lahman`, `tidyverse` and R. There will be issues with the `Lahman` and `tidyverse` citations:

```{r incorrect-file, eval=FALSE}
@Manual{,
  title = {Lahman: Sean 'Lahman' Baseball Database},
  author = {Michael Friendly},
  year = {2021},
  note = {R package version 9.0-0},
  url = {https://CRAN.R-project.org/package=Lahman},
}

@Article{,
  title = {Welcome to the {tidyverse}},
  author = {Hadley Wickham},
  year = {2019},
  journal = {Journal of Open Source Software},
  volume = {4},
  number = {43},
  pages = {1686},
  doi = {10.21105/joss.01686},
}

@Manual{,
  title = {R: A Language and Environment for Statistical Computing},
  author = {{R Core Team}},
  organization = {R Foundation for Statistical Computing},
  address = {Vienna, Austria},
  year = {2019},
  url = {https://www.R-project.org/},
}
```

```{r two-issues}
check_bibtex_file("incorrect_example.bib", c("Lahman", "tidyverse", "base"))
```




