---
title: "The `check_bibtex_citations` file"
author: "Matthew Wankiewicz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The `check_bibtex_citations` file}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(citationcheckR)
```

## About the function

The `check_bibtex_citations` function allows users to check if a BibTeX citation they have matches up with  R's citation. The 

## Using the function

### Matching function

The first case we will see is if the two citations match each other.

```{r matching}
test_citation <- create_citations("citationcheckR", include_r = F)

check_bibtex_citations(test_citation, "citationcheckR")
```

Since there are no differences between the citation given and R's citation, we receive the "No citation issues found!" message.

### One mismatch

```{r one-mismatch}
test_citation <- "@Manual{,
  title = {citationcheckR: Citation Checker for R},
  author = {Matthew Wankiewicz},
  year = {2010},
  note = {R package version 0.1.0},
  url = {https://github.com/matthewwankiewicz/citationcheckR},
}"

check_bibtex_citations(test_citation, "citationcheckR")
```

We can see that when entries do not match, the function will tell us which entry does not match and what the correct entry is. 

### Multiple Mismatches

```{r multiple-mismatches}
test_citation <- "@Manual{,
  title = {citationcheckR: Citation Checker for R},
  author = {Matthew},
  year = {2020},
  note = {R package version 0.1.0},
  url = {https://github.com},
}"

check_bibtex_citations(test_citation, "citationcheckR")
```

As we can see, when multiple entries are mismatched, the function will tell us what the issues are, one by one.

### Mismatched Packages

```{r}
test_citation <- create_citations("base")

check_bibtex_citations(test_citation, "citationcheckR")
```

When the packages are not the same the function will treat it as entries which are not matched.
