---
title: "The `create_citations` function"
author: "Matthew Wankiewicz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The `create_citations` function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(citationcheckR)
```

## About the Function

`create_citations` was made to speed up the process of getting citations for your R papers, reports or anything else. Instead of having to run `citation` multiple times, you can run `create_citations` once to get all of your citations done quickly. The citations are returned in the console or under your R chunk, making it easy to copy and paste.

## Using the function

### Making the citations

There are two ways to gather the packages used to create citations. The first way to gather the packages is to leave the `packages` argument empty. Doing this tells the function to take any package that has been loaded into your R session and create citations for it. 

```{r citations-empty-arg}
create_citations()
```


The other way to create citations is to fill the citations arugment with the packages you want to get citations for.

```{r citations}
create_citations(c("Lahman", "tidyverse", "DoSStoolkit"))
```


### Including R

As you may have noticed, the citations that were returned included a citation for R. This is done by default and can be turned off using `include_r = FALSE`. 

```{r include_r}
create_citations(c("Lahman", "tidyverse", "DoSStoolkit"), include_r = FALSE)
```

## Changing Citation Formats

By default, `create_citations` will return citations as bibTeX, but this can be changed by setting `format = 'text'`

```{r}
create_citations(c("Lahman", "tidyverse", "DoSStoolkit"),
                 include_r = FALSE, format = "text")
```

